Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-09 paper.tex
Gingerizing to Experimental setup for issue #55

Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.

@@

The application of FS also aims to reduce the complexity of the obtained 
forecasting models themselves, which, in turn, implies a reduction in the 
computational time for building these models. This has been a key 
factor in this work, because one of the objectives is to obtain `easily' 
interpretable decision models, which can be useful for human experts (publishers).
Regarding the algorithm, running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}; however, this is a secondary objective in this work.

FS is one of the ways of performing a feature reduction, the other one is 
feature extraction \cite{kittler1986feature}. 
Feature extraction is a `transformation-based approach', therefore
it transforms the original meaning of the features. This method
involves creating a subset of new features by combining the
existing ones; thus it is employed when the semantics of the
original dataset will not be needed by any future process. On the
contrary, FS attempts to retain the meaning of the
original feature set. It is part of what is called semantic-preserving
techniques, known as `selection-based approaches' \cite{liu1998feature}. 
In the problem this work addresses, it is very important to maintain the 
semantics of initial variables set, and therefore just FS methods 
have been applied.

@@

Correlation coefficient, error measures and time to build the model have been 
computed for every method. Obtained results are presented in 
Figure \ref{fig:all_publishers_no_fs}
(detailed numeric results can be seen in Table \ref{tab:all_publishers_no_fs}
in the appendix of tables at the end of this paper).

@@

kNN is the fastest method used in this study in terms of training time, as it 
is the simplest one. However, the model is slow when classifying large number of 
training examples, and it exhibits a poor generalisation ability since it does 
not learn enough from the training data.

@@

MLP also gets a very good correlation coefficient, however it takes the largest time to built the models, and obtains high error measures. ELM shows a good balance, since it is very fast in the training phase (the second faster) and yields good results according to the correlation and the error metrics.

As a first conclusion, paying attention both to the cost in time to obtain the 
forecasting models and their accuracy, the M5P model would be the most adequate 
to solve the problem of how many books should be printed when a new book is 
published considering all the pre-sales data. Therefore this forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.

@@

Thus, the chosen map to represent the data has $26 \times 16$ neurons and an hexagonal neighbourhood topology.  The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.

Figure \ref{fig:componentplanes} shows the U-matrix along with the component 
planes analysis resulted from SOM training. The term component refers in SOM 
to a variable or feature of the problem.
The component planes in Figure \ref{fig:componentplanes} show the trend of 
values of the prototype vectors of the SOM map units. These values are represented 
as colours. The colourbar on the right of each component plane shows the indication 
of each colour. On the other side, the U-matrix on the top
left corner shows the distances between the adjacent units. It is
important to note that high values in the matrix indicates large
distance between the units of the map. It can be noticed also that
there are more hexagons in the U-matrix than component planes since
the distances between units are also represented as inter-neuron hexagons.

>>>>

Therefore, after the data has been collected and initially preprocessed (as described in the previous section), other preprocessing techniques have been applied, such as Feature Selection (FS) \cite{kittler1986feature}, since it is an effective dimensionality reduction technique, able to discard less relevant or non-useful features \cite{Krishnapuram2004,Chen2011_FS_PTS}.

@@

The application of FS also aims to reduce the complexity of the obtained 
forecasting models themselves, which, in turn, implies a reduction in the 
computational time for building these models. This has been a key 
factor in this work, because one of the objectives is to obtain `easily' 
interpretable decision models, which can be useful for human experts (publishers).
Regarding the algorithm, running time grows with the number of
features, making it impractical for problems with a large number of features 
\cite{Selvakuberan2008}; however, this is a secondary objective of this work.

FS is one of the ways of performing a feature reduction, the other one is 
feature extraction \cite{kittler1986feature}. 
Feature extraction is a `transformation-based approach', therefore
it transforms the original meaning of the features. This method
involves creating a subset of new features by combining the
existing ones; thus it is employed when the semantics of the
original dataset will not be needed by any future process. On the
contrary, FS attempts to retain the meaning of the
original feature set. It is part of what is called semantic-preserving
techniques, known as `selection-based approaches' \cite{liu1998feature}. 
In the problem this work addresses, it is very important to maintain the 
semantics of the initial variables set, and therefore just FS methods 
have been applied.

@@

Correlation coefficient, error measures and time to build the model have been 
computed for every method. The obtained results are presented in 
Figure \ref{fig:all_publishers_no_fs}
(detailed numeric results can be seen in Table \ref{tab:all_publishers_no_fs}
in the appendix of tables at the end of this paper).

@@

kNN is the fastest method used in this study in terms of training time, as it 
is the simplest one. However, the model is slow when classifying a large number of 
training examples, and it exhibits a poor generalisation ability since it does 
not learn enough from the training data.

@@

MLP also gets a very good correlation coefficient. However, it takes the largest time to built the models, and obtains high error measures. ELM shows a good balance, since it is very fast in the training phase (the second fastest) and yields good results according to the correlation and the error metrics.

As a first conclusion, paying attention both to the cost in time to obtain the 
forecasting models and their accuracy, the M5P model would be the most adequate 
to solve the problem of how many books should be printed when a new book is 
published considering all the pre-sales data. Therefore, this forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.

@@

Thus, the chosen map to represent the data has $26 \times 16$ neurons and a hexagonal neighbourhood topology.  The best SOM training results have been obtained with a final quantisation error of 0.691 and topographic error of 0.046.

Figure \ref{fig:componentplanes} shows the U-matrix along with the component 
planes analysis resulted from SOM training. The term component refers in SOM 
to a variable or feature of the problem.
The component planes in Figure \ref{fig:componentplanes} show the trend of 
values of the prototype vectors of the SOM map units. These values are represented 
as colours. The colourbar on the right of each component plane shows the indication 
of each colour. On the other side, the U-matrix on the top
left corner shows the distances between the adjacent units. It is
important to note that high values in the matrix indicate large
distance between the units of the map. It can be noticed also that
there are more hexagons in the U-matrix than component planes since
the distances between units are also represented as inter-neuron hexagons.
